\bfseries How do sailboats work? A simple momentum-transport model

### 2024-08-25 paper/main.tex

HOGG: Note about how it feels. Is this repetitive with comments above? If so, remove them and replace with references down to this Section.

>>>>

LEHMAN: AN OBSERVATION ABOUT FIG.~2: THE DWFTTW PARAMETER SPACE LOOKS SYMMETRICAL WITH UPWIND SAILING! (IS THIS STRICTLY TRUE?) THIS MAKES SOME SENSE: ONCE YOU'RE GOING DWFTTW, YOU HAVE A HEADWIND THAT IS THE SAME AS IF YOU WERE SAILING UPWIND. BUT THE VELOCITY RELATIVE TO THE WATER IS DIFFERENT IN THE TWO CASES, SO WHAT RESTORES THE SYMMETRY? MAYBE FIG.~7 PROVES THAT THE SYMMETRY IS ACCIDENTAL.

LEHMAN: IS ONE WAY TO THINK ABOUT DWFTTW THAT SOME OF THE "USELESS" FORCE OF THE WIND ON THE SAIL/HULL (I.E.~PERPENDICULAR TO DIRECTION OF TRAVEL) GETS REDIRECTED TO "USEFUL" FORCE BY THE ANGLE OF THE KEEL AGAINST THE WATER? IF SO, THIS WOULD SEEM TO REQUIRE THE TOTAL WIND-SAIL FORCE AT A "FAST" ANGLE TO BE GREATER THAN THE WIND-SAIL FORCE DIRECTLY DOWNWIND. NOT SURE WHY THIS WOULD BE TRUE, BUT MAYBE MY CONFUSION COULD BE HELPFUL IN DECIDING HOW TO WRITE THIS SECTION...

HOGG: Possible Note about how it feels. Is this repetitive with comments above? If so, remove them and replace with references down to this Section.
